\chapter*{Lecturers}

\section*{Koray Kavalı}
PhD Candidate,
University College London,
United Kingdom

E-mail: kkavakli@ku.edu.tr

\href{https://scholar.google.com/citations?user=rn6XtO4AAAAJ&hl=en&oi=ao}{Koray Kavaklı} is a PhD student in Computational Light Laboratory at University College London.
He has completed his M.Sc. degree in Optical Microsystems Laboratory at Koç University.
He received his B.S. degrees from Koç University Electrical and Electronics Engineering and B.A. in Business Administration.
During his M.Sc. studies, he worked as a research engineer in CY Vision, Turkey. He worked as a research engineer in CY Vision, Istanbul.
His research includes developing computer-generated holographic displays with novel graphics pipelines, light transport modelling, and biomedical applications of the holographic displays.

\section*{David Robert Walton}
Postdoctoral Researcher, 
University College London,
United Kingdom

E-mail: david.walton.13@ucl.ac.uk

\href{https://drwalton.github.io/}{David Robert Walton} is a postdoctoral researcher working in the Virtual Environments and Computer Graphics group at University College London (UCL) in the United Kingdom. He previously completed an EngD working with UCL and Imagination Technologies on computer vision and rendering techniques for improved lighting in augmented reality. His current research focuses on computer graphics, novel displays and human perception, particularly how properties of visual perception can aid in developing efficient graphics algorithms and novel display hardware.


\section*{Nick Antipa}
Assistant Professor,
University of California, San Diego, United States of America

E-mail: nantipa@eng.ucsd.edu

\href{http://nickantipa.com/}{Nick Antipa} is an assistant professor in Electrical and Computer engineering where his lab focuses on computational imaging.
He received his PhD in Computational Imaging at UC Berkeley in the Electrical Engineering and Computer Sciences department with Laura Waller and Ren Ng.
Prior to his time at Berkeley, Nick worked as an optical engineer at Lawrence Livermore National Lab, designing 3D metrology equipment in support of the National Ignition Facility.
Nick received his MS in Optics from the University of Rochester in 2009, and BS in Optical Science and Engineering at UC Davis in 2008.

\section*{Rafał Mantiuk}
Professor, University of Cambridge, United Kingdom

E-mail: rafal.mantiuk@cl.cam.ac.uk

\href{http://www.cl.cam.ac.uk/~rkm38/}{Rafał K. Mantiuk} is a Professor of Graphics and Displays at the Department of Computer Science and Technology, the University of Cambridge in the United Kingdom.
He received PhD from the Max-Planck Institute for Computer Science in Germany.
His recent interests focus on computational displays, rendering and imaging algorithms that adapt to human visual performance and deliver the best image quality given limited resources, such as computation time or bandwidth.
He contributed to early work on high dynamic range imaging, including quality metrics (HDR-VDP), video compression and tone-mapping.

\section*{Douglas Lanman}
Director of Display Systems Research, Facebook Reality Labs, United States of America

E-mail: douglas.lanman@fb.com

\href{https://alumni.media.mit.edu/~dlanman/}{Douglas Lanman} is the Director of Display Systems Research at Reality Labs, where he leads investigations into advanced AR/VR display and imaging technologies.
He received a B.S. in Applied Physics with Honors from Caltech in 2002 and M.S. and Ph.D. degrees in Electrical Engineering from Brown University in 2006 and 2010, respectively.
He was a Senior Research Scientist at NVIDIA Research from 2012 to 2014, a Postdoctoral Associate at the MIT Media Lab from 2010 to 2012, and an Assistant Research Staff Member at MIT Lincoln Laboratory from 2002 to 2005.

\newpage

\section*{Kaan Akşit}

Associate Professor,
University College London,
United Kingdom

E-mail: k.aksit@ucl.ac.uk

\href{https://kaanaksit.com}{Kaan Akşit} is an Associate Professor in the computer science department at University College London, where he leads the Computational Light Laboratory.
Kaan received his PhD degree in electrical engineering at Koç University, Turkey, in 2014. 
He received an M.Sc. degree in electrical power engineering from RWTH Aachen University, Germany, in 2010.
He obtained a B.S. degree in electrical engineering from Istanbul Technical University, Turkey, in 2007. 
He worked as a research intern in Philips Research, the Netherlands, and Disney Research, Switzerland, in 2009 and 2013, respectively. 
In addition, he was a scientist at NVIDIA, the USA, between 2014 and 2020.
