\chapter*{Course Overview}


\section*{5 minutes: Welcome and Introductions}
\textit{Kaan Akşit}
Welcoming the audience, Describing the aims and objectives of the course, Highlighting the target audience and Introducing lecturers.


\section*{20 minutes: Keynote on future interfaces}
\textit{Douglas Lanman}
An analysis of issues in the current day vision and visuals, and a prime outlook on future's devices.


\section*{30 minutes: Next-generation Compressive Sensing: Lensless Cameras}
\textit{Nick Antipa}
A survey on state-of-art research on lensless cameras with research highlights and their promises for future's interfaces.
Basic concepts and descriptions will be provided related to lensless cameras.
In the next step,an interactive coding session will be provided to demonstrate how to process images from a lensless camera using the Alternating Direction Method of Multipliers (ADMM), vanilla Gradient-Descent (GD) and Fast Iterative Shrinkage-Thresholding Algorithm (FISTA) methods.


\section*{45 minutes: Next-generation Computational Displays: Holographic Displays}
\textit{Kaan Akşit, Koray Kavaklı and David Robert Walton}
A survey on state-of-art research on holographıc dısplays wıth research highlights and their promises for future's interfaces.
Basic concepts and descriptions will be provided related to holographic displays.
The survey is followed by an interactive coding session to demonstrate how to create computer-generated holograms for a standard holographic display using Gerchberg-Saxton (GS), Vanilla Gradient-Descent (GD) and Stochastic Gradient Descent (SGD).
In addition, an interactive coding session to demonstrate how to derive a perceptually guided gaze-contingent loss function and how to use such functions on a standard holographic display will also be provided.


\section*{30 minutes: Practical models of Perception in Graphics}
\textit{Rafał Mantiuk}
A brief tutorial on modelling the visual quality using psychophysical models of contrast sensitiviity, luminance masking and contrast masking.
The tutorial will be illustrated with examples and ready-to-use code.
